How Important are Usage Examples in REST API Documentation?

### 2017-01-30 bare_conf.tex
tasks

\subsection{Study Design} % (fold)
\subsubsection{Tasks} % (fold)
  For each task, define the task. Information that provided to the participants and what is required to perform it successfully.

>>>>

\subsection{Study Design} % (fold)
\subsubsection{Tasks} % (fold)

The participants are requested to perform a total of six tasks using the API including one practice task. All of the tasks are related to a single API element, $Post$. The tasks get progressively difficult, and all but the last task can be performed independently of each other. Participants are requested to limit the total time on the study to a maximum of one hour. Participants are encouraged to proceed to the next task when they are either satisfied about or stuck on the right answer.

To use a REST API, the API client developers need to work with the following four inputs over HTTP:

\begin{itemize}
  \item I1. Request method
  \item I2. Request URL
  \item I3. Request headers
  \item I4. Request body
\end{itemize}

To verify the response of an API call, the API client developers can use HTTP response headers and/or HTTP response body. To perform the tasks, the participants are required to use one or more of the inputs I1-4. In the following paragraphs, we describe each task with it's description and the intended test scenario against the aforementioned API input and output information. For each of the tasks, the participants are required to use the same WordPress REST API and its documentation.

\textbf{T1: ListAllPostsTask}. We ask the participants to use the WordPress REST API following its documentation to get a list of the blog posts from a live WordPress site. This is the practice task, and the inputs to answer this task are pre-filled for the participants. It allows the participants to understand the tools used for this study as well as get familiarity with the Post API. The answer for this task makes use of I1 and I2.

\textbf{T2: FilterPostsByAuthorTask.} The participants are asked to use the API to filter the list of posts by an author given the author's user name. To answer this correctly, the participants are required to first make an API call to get the numeric ID of the author given the string based user name. Then, the ID needs to be used on the Post API to filter posts by the author. This task allows us to understand the impact of usage examples on API client developers when multiple API calls need to be made to perform a task using the API. Inputs I1-2 are required to complete this task successfully.

\textbf{T3: ExcludePostsByIdsTask.} We ask the participants to use the API to get a list of all posts excluding posts with IDs 1 and 4. Participants need to use the inputs I1-2, and use a desired format on I2 to pass an array of IDs as a parameter. This task allows us to understand how API client developers identify the format for using an array within the URL with respect to the usage examples in the API documentation.

\textbf{T4: FindTotalPostsTasks.} This task requires the participants to use the API to find a total number of posts. Participants need to use the inputs I1-2 and inspect the HTTP response headers to successfully complete this task. This task allows us to understand how API client developer productivity is affected with respect to missing examples about HTTP response headers in the API documentation.

\textbf{T5: PublishPostTask.} We ask the participants to use the API to publish a blog post with a specific title, content, and a published date. To successfully complete this task, the participants are required to use all four input types and inspect both the HTTP response header and the response body. Additionally, the participants are required to use a specific date format that the API accepts as a valid format for date specification. Answers to this task allows us to study API client developer productivity with respect to the usage examples lacking details about the inputs I3-4.

\textbf{T6: UpdatePostTask.} We ask the participants to use the API to update a blog post that they published in T5 with a new excerpt. Similar to T5, this task requires the use of inputs I1-4, but with different values for the inputs. This task allows us to understand API client developer productivity on inter-dependent tasks with respect to usage examples.

To summarize, the tasks allow us to understand how REST API client developers approach API tasks of different complexity levels involving various input types and available output information with respect to the usage examples in the API documentation.
